Differentially Private Bayesian Inference

### 2018-03-12 main.tex
dilation property proof
update dilation property proof

>>>>

\section{Dilation Property of Laplace Noise}
\label{sec_Dila}
\begin{proof}
We take 1-dimensional Laplace distribution, $h(z) = \frac{1}{2} e^{-|z|}$.
The dilation property is:
\begin{equation*}
Pr[z \in S] \leq e^{\frac{\epsilon}{2}} Pr[z \in e^{\lambda} S] + \frac{\delta}{2}
\end{equation*}
In this case, we have $\alpha = \frac{\epsilon}{2}$, $\beta = \frac{\epsilon}{2 \rho_{\delta/2}(|z|)}$ or $ \frac{\epsilon}{2 ln(2/\delta)}$. We have some prior knowledge that $|\lambda| \leq \beta$.

\begin{itemize}
	\item \textbf{case 1: $\lambda > 0$}

	\begin{equation*}
	\begin{split}
	\because\ 		& 	h(e^{\lambda} z) =  \frac{1}{2} e^{-|e^{\lambda} z|} < \frac{1}{2} e^{-|z|} = h(z)\\
	\therefore\		& 	\frac{Pr[z \in e^{\lambda} S]}{Pr[z \in S]} 
						= \frac
						{\int_{e^{\lambda} S}{} \frac{1}{2}e^{-|z|} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|} dz} 
						= \frac
						{\int_{S}{} \frac{1}{2}e^{-|e^{\lambda}z|} e^{\lambda} dz}
						{\int_{S}{} \frac{1}{2}e^{-|z|}dz} \\
					&	= \frac{e^{-|e^{\lambda}z|} e^{\lambda}}{e^{-|z|}}
						= \frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}
						\leq e^{\lambda}\\
	\therefore\		&	ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)})
						\leq \lambda \\
	\because\		&	\\
	\end{split}
	\end{equation*}

	\item \textbf{case 2: $\lambda < 0$}
	\begin{equation*}
	\begin{split}
	\because\	& \frac{h(e^{\lambda} z)}{h(z)} = exp(|z|(1 - e^{\lambda})) \leq |\lambda|\\
	\therefore\	& ln(\frac{e^{\lambda} h(e^{\lambda} z)}{h(z)}) \leq |z||\lambda|\\
	\end{split}
	\end{equation*}

\end{itemize}
